The Driving Forces of API Evolution

### 2015-05-25 thesis/paper.tex
Smaller changes

\begin{abstract}
%Motivation
Evolving an Application Programming Interface (API) is a precipitous activity, mainly because of the great implications modifications can have on the users of it. As the usage of APIs increases, software development organisations must take an empirical and scientific approach to the way they manage the evolution of their APIs. 
%Problem
If no attempt at analysing or quantifying the evolution of an API is made, there will be a lacking understanding of the evolution, and possible improvements to the maintenance strategy will be difficult to identify. We believe, that long-standing software evolution theories can provide additional insight to the field of APIs, and be of great use to companies maintaining APIs. 
%Method
In this case study, we conduct a qualitative investigation on what drives the evolution of an industry company's existing API, by examining two versions of the API code. The changes were analysed based on two software evolution theories, and the extent to which we could reverse engineer the change decisions were tested by interviewing the architect of the API. 
%Results
The results of this analysis show that the largest driving force of API evolution is the desire for new functionality. Our findings which show that changes happen sporadically, rather than continuously, invalidate a law of software evolution, in the context of APIs. We also found that change decisions were highly reverse engineerable, and identified the feedback loop of an API to be the most major area of improvement. 
\end{abstract}

@@

              \begin{enumerate}
              \item Inspect source code  
              \item Inspect accompanying documentation 
              \item Generate Hypotheses 
              \item Conduct Interview 
              \item Analyse source code
              \end{enumerate} \\

              \begin{enumerate}
              \item Analyse interviews 
              \item Classify trends according to types 
              \item Compare classifications against interview responses 
              \item Analyse from software evolution theory point of view 
              \item Validate Hypotheses 
              \end{enumerate} \\

>>>>

\begin{abstract}
%Motivation
Evolving an Application Programming Interface (API) is a precipitous activity since(!!!) modifying an API can significantly impact its users. As the usage of APIs increases, software development organisations must therefore take an empirical and scientific approach to the way they manage the evolution of their APIs. 
%Problem
If no attempt at analysing or quantifying the evolution of an API is made, there will be a lacking understanding of the evolution, and possible improvements to the maintenance strategy will be difficult to identify. We believe, that long-standing software evolution theories can provide additional insight to the field of APIs, and be of great use to companies maintaining APIs. 
%Method
In this case study, we conduct a qualitative investigation on what drives the evolution of an industry company's existing API, by examining two versions of the API code. The changes were analysed based on two software evolution theories, and the extent to which we could reverse engineer the change decisions were tested by interviewing the architect of the API. 
%Results
The results of this analysis show that the largest driving force of API evolution is the desire for new functionality. Our findings which show that changes happen sporadically, rather than continuously, invalidate a law of software evolution, in the context of APIs. We also found that change decisions were highly reverse engineerable, and identified the feedback loop of an API to be the most major area of improvement. 
\end{abstract}

@@
